An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-04-06 poly-embed-journal/poly-embed-journal.tex
Adding in construction of minimal representative set

\usepackage{mathtools, amsmath, amssymb, amsthm, graphicx, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}
\usepackage{wrapfig}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

@@

\jessie{Adding new statements}
\begin{definition}
	Suppose a generic loss $L : \R \to \reals^\Y$ is given with polyhedral risk $-\risk{L}$.
	Construct the set $\Sc(L)$ as follows:
	Each facet $F$ of the epigraph of negative risk $E_L$ must be full dimensional by definition of a facet.
	Take $p \in \inter{F}$, and observe that it must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$.
	Add $u$ to $\Sc(L)$, and repeat, iterating over each of $E_L$'s finitely many facets.
\end{definition}

\begin{proposition}
	If loss $L: \R \to \reals^\Y_+$ has polyhedral risk, $\Sc(L)$ is a minimal representative set for $L$.
\end{proposition}
\begin{proof}\jessiet{I don't like this proof, but meh.}
	If $\Sc(L)$ was not a minimal set, then we could remove some $s$ from $\Sc$ such that $\Sc' := \Sc \setminus \{s\}$ is also a representative set for $L$.
	By construction, we have some distribution $p$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$.
	We particularly have $\Gamma(p) \cap \Sc' = \emptyset$, since any other element $s'$ of $\Sc'$ being in $\Gamma(p)$ would imply $p \mapsto (p, L(s'))$ also supports $E_L$, but this hyperplane must be unique, and therefore either $s$ or $s'$ would not be in $\Sc$.
\end{proof}

@@

\proposedadd{For the reverse implication, assume $\risk{L} = \risk{\ell}$ are polyhedral functions.  Since $\risk{\ell}$ is polyhedral, the epigraph of its negation, $E_\ell$, has a finite set of facets, which by definition have well-defined interiors.  For each facet, there must then be some distribution $p_r$ and report $r \in \R$ such that the hyperplane $p_r \mapsto (p_r, \inprod{p_r}{-\ell(r)})$ uniquely supports $E_\ell$.  Form $\Sc$ from the set of such reports $r$, iterating over each facet.  We have $\Sc$ representative for $\ell$ since the union of projected epigraph facets equals the simplex, and these facets and their projections are closed. Therefore, every $p \in \simplex$ is contained in some facet of the epigraph, and thus there is some $r \in \Sc$ so that $r \in \gamma(p)$.
As the risks are equal, the same is true for $E_L$, e.g., for each facet, there is some $u_r$ so that $p_r \mapsto (p_r, \inprod{p_r}{L(u_r)})$, and one can construct the embedding $\varphi: r \mapsto u_r$ for each $r \in \Sc$.}

\proposedadd{To verify matching losses, observe $\risk \ell (\delta_y) = \risk L (\delta_y)$ for each $y \in \Y$, and these risks are attained by some report $r$ and its embedding $u_r$, respectively.
Matching optimality is true by construction, since the optimal reports support the epigraph of negative Bayes risk on exactly the same distributions, meaning a report and its embedding are optimal at exactly the same distributions.}
\end{proof}

@@

\raft{I wonder if we should demote this to a corollary.  We can write the proof of the reverse implication in Proposition~\ref{prop:embed-bayes-risks} like this: first show that if $\risk{L}$ is polyhedral, there is a finite $\U$ which is representative for $L$.  Then show that if $\risk{\ell} = \risk{L}$ then there is some $\Sc$ that is bijective to the particular $\U$ we constructed.  I'm not sure how this will go, but perhaps worth a try, since it would avoid the proof duplication too!}
\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss $\ell : \R \to \reals^\Y_+$ if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and polyhedral.
  For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  \proposedadd{Form the set $\Sc$ by iterating over the facets of $E_L$, the epigraph of $-\risk{L}$.
  For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.  Take $\Sc$ to be the collection of such reports $u$, and observe $\Sc$ is representative for $L$.  By Corollary~\ref{cor:representative-embeds-restriction}, $L$ embeds $L|_\Sc$, which is finite by construction.}
%  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
%  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
%  Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
\end{proof}

@@

\proposedadd{Moreover, to construct an embedding of dimension $n-1$ instead of $n$ (see~\citet{finocchiaro2020embedding} for significance of dimension),  we use the same trick as in the proof of Proposition~\ref{prop:embed-bayes-risks}.
Consider some invertible linear transformation $A : \reals^n \to \reals^{n-1}$ that reduces to an affine subspace.
Take $L' : \reals^{n-1} \to \reals^\Y$ as $x \mapsto L(A^{-1}(x))$ and $L$ defined as above, so that $\inprod{\ell(r)}{p} = \inprod{L(\varphi(r))}{p} = \inprod{L'(A^{-1}(\varphi(r)))}{p} $ for all $p \in \simplex$.
The Bayes risks $\risk{L}(p)$ and $\risk{L'}(p)$ are equal for all $p \in \simplex$; thus, the result holds in $n-1$ dimensions as well.}\jessiet{Leaving this change in the macro for proofreading.}

@@

\jessiet{New to journal version}
\begin{lemma}\label{lem:embed-defs-equiv}
	%  \raft{Introduce $L$}
	Let $L : \reals^d \to \reals^\Y_+$ be a loss function \proposedadd{whose infimum is attained in expectation for all $p \in \simplex$}\raft{Ah, good call! \#burn}.
	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell:\R \to \reals^\Y_+$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
\end{lemma}
\begin{proof}
	\raft{All the important pieces are here, but take it slower.  State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.  Now very similar to the proof of Prop 1 forward direction.}}
	Consider the embedding $\varphi$ given by the property embedding and take the discrete loss $\ell:r \mapsto L(\varphi(r))$.
	Now, we claim that $L$ embeds $\ell$, and by Proposition~\ref{prop:embed-bayes-risks}, we can simply show $\risk{L} = \risk{\ell}$, and the risks being polyhedral follows from $\ell$ being discrete.

	First, we show that for all $p \in \simplex$, we have $(1) \inf_{u \in \reals^d}\inprod{p}{L(u)} = (2) \inf_{r \in \R}\inprod{p}{L(\varphi(r))}$, and the equality of risks follows.
	$(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$ and definition of infimum. 
	Consider that if we had $(1) < (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$ \jessie{BUG: NEED THE INFIMUM TO BE ATTAINED}, and therefore, we would have $\gamma(p) = \emptyset$, yielding a contradiction. 
	This gives us $(1) = (2)$, so we have $\risk{L} = \risk{L|_{\varphi(\R)}} = \risk{\ell}$.
	%
	%Now consider the property $\Gamma' := p \mapsto \Gamma(p) \cap \varphi(\R)$.
	%We have $\Gamma'$ nondegenerate since $\Gamma$ embedding $\gamma$ implies that, for all $p \in \simplex$, there is some $r \in \R$ such that $\varphi(r) \in \Gamma(p)$.
	%Therefore, for all $p \in \simplex$, we have $\inf_{r \in \R}\inprod{p}{L(\varphi(r))} = \inf_{r \in \R} \inprod{p}{\ell(r)}$, which yields $\risk{L|_{\varphi(\R)}} = \risk{\ell}$.
	%Chaining the two equalities, we now have $\risk{L} = \risk{\ell}$.

@@

By Lemma~\ref{lem:embed-defs-equiv}, we can work directly with properties and set aside the losses which elicit them, which is often more convenient.
Moreover, we can assume that finite properties are non-redundant without much loss of generality.
\begin{definition}[Finite property]
	\jessie{Should be earlier}
	A property $\gamma:\simplex\toto\R$ %is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.  $\gamma$ 
	is \emph{finite} if $\R$ is a finite set.
\end{definition}

@@

\btw{JESSIE: Figures/an example might help clarify this}
When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
\jessiet{This lemma new to journal version}
\begin{lemma}\label{lem:embedded-level-sets-trim}
	Let $\Gamma$ be an elicitable property.
	If $\Gamma$ embeds a (non-redundant) finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)\proposedadd{=\trim(\gamma)}$.
	\proposedadd{RETRY: Let $\Gamma$ be an elicitable property.
		If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then there is a set $\Sc$ such that $\Sc$ is representative for $\gamma$\jessiet{Need to define this, technically} and $\{\gamma_r : r \in \Sc\} = \{\Gamma_u : u \in \varphi(\Sc)\} = \trim(\Gamma)=\trim(\gamma)$.}
\end{lemma}
\begin{proof}
	Let $L$ elicit $\Gamma$.
	Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
	Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
	%\raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
	As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional in $\affhull(\simplex)$. 
	For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
	Moreover, we have $\{\gamma_r : r \in \R\} = \{\Gamma_{\varphi(r)} : r \in \R\}$ as a corollary since this is true for each $r \in \R$.
	\raft{The main action is here.  (1) Epigraph of $-\risk{L}$. (2) There is really only one case: every level set is a face of the power diagram, which must be contained (weakly, so $\subseteq$) in a facet. (3) To show that level sets are faces, you'll want to appeal to some piece of a proof in the prev section.}
	Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $-\risk{L}$, which is convex, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered as faces of the epigraph of $-\risk{L}$, and therefore a face of the induced power diagram.
	Therefore, we remove lower-dimensional faces, as they are proper subsets of the level sets of embedded reports, and conclude such $\Gamma_u \not \in \trim(\Gamma)$.
	% in one of two cases:
	%First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
	%Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.

@@

\proposedadd{First, construct $\Sc$ as in the proof of Proposition~\ref{prop:embed-bayes-risks}; this is a minimal representative set in the sense that removing any element $r$ corresponding to the facet $F_r$ from $\Sc$ leads to $\gamma(p) \cap \Sc = \emptyset$ for all $p \in \inter{F_r}$. Moreover, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, and therefore $\gamma_r = \Gamma_{\varphi(r)}$, yielding $\{\gamma_r \mid r \in \Sc\} = \{\Gamma_{\varphi(r)} \mid r \in \Sc\}$ as this is true for all $r \in \Sc$.}

\proposedadd{TO SHOW: $T := \{\gamma_r \mid r \in \Sc\} = \trim(\gamma)$. 
	First, if $\gamma_r \in T$, then it is not a subset of any level set as $\gamma_r$ is full-dimensional in the simplex as it corresponds to a facet of the epigraph of the negative risk $E_\ell$, and the supporting hyperplane is therefore unique.
	Now, if $\theta \in \trim(\gamma)$, then there is some report $r'$ such that $\theta = \gamma_{r'}$.
	If $r' \not \in \Sc$, we want to claim there is some $r$ such that $\gamma_{r'} = \gamma_r$.
	As $\theta$ is a maximal level set, it has a nonempty interior.
	Therefore, for any $p \in \inter{\theta}$ (and one such $p$ must exist), the hyperplane $p \mapsto (p, \ell(r'))$ uniquely supports the hyperplane.
	If $r' \not \in \Sc$, then there must be some $r \in \Sc$ such that $p \mapsto (p, \ell(r))$ also supports the same facet of $E_\ell$; if no such $r \in \Sc$ existed, we would contradict our claim that $\Sc$ is representative for $\ell$.
Similarly, we have $\{\Gamma_u \mid u \in \varphi(\Sc)\} = \trim(\Gamma)$ by the same logic.}
\end{proof}

>>>>

\usepackage{mathtools, amsmath, amssymb, amsthm, graphicx, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\definecolor{darkgreen}{rgb}{0.0,0.3,0.0}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}
\usepackage{wrapfig}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

@@

\jessie{Adding new statements}
\begin{definition}[$\Sc(L)$]\label{cons:rep-set}
	Suppose a generic loss $L : \R \to \reals^\Y$ is given with polyhedral risk $-\risk{L}$.
	Construct the set $\Sc(L)$ as follows:
	Each facet $F$ of the epigraph of negative risk $E_L$ must be full dimensional by definition of a facet.
	Take $p \in \inter{F}$, and observe that it must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$.
	Add $u$ to $\Sc(L)$, and repeat, iterating over each of $E_L$'s finitely many facets.
\end{definition}

\begin{proposition}
	If loss $L: \R \to \reals^\Y_+$ has polyhedral risk, $\Sc(L)$ is a minimal representative set for $L$.
\end{proposition}
\begin{proof}\jessiet{I don't like this proof, but meh.}
	First, we have to show that $\Sc(L)$ is a representative set.
	As facets are closed and the hyperplane $p_F \mapsto (p_F, \inprod{p_F}{L(u_F)})$ supports $E_L$ (epigraph of negative risk) over the entire facet (and therefore $\Gamma(p) \cap \Sc(L) \ni u_F$ for all $p$ such that the hyperplane supports $E_L$ at $p$), we have $\Sc(L)$ representative for $L$.

	If $\Sc(L)$ was not a minimal set, then we could remove some $s$ from $\Sc$ such that $\Sc' := \Sc \setminus \{s\}$ is also a representative set for $L$.
	By the construction of $\Sc$ over facets of $E_L$, we have some distribution $p$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$.
	We particularly have $\Gamma(p) \cap \Sc' = \emptyset$, since any other element $s'$ of $\Sc'$ being in $\Gamma(p)$ would imply $p \mapsto (p, L(s'))$ also supports $E_L$, but this hyperplane must be unique, so these are equal.
	By construction of $\Sc$, we must have only added at most one of these to the set.
	Therefore, $\Sc(L)$ is a minimal representative set.
\end{proof}

@@

\proposedadd{ALTERNATE PROOF FOR REVERSE IMPLICATION: 
	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.  
	Construct $\Sc := \Sc(\ell)$ as in Definition~\ref{cons:rep-set}, and $\U := \Sc(L)$, with the embedding $\varphi : r \mapsto u_r$ if the hyperplanes $p \mapsto (p, \inprod{p}{\ell(r)})$ and $p \mapsto (p, \inprod{p}{L(u_r)})$ are equal.
	Such an embedding is well-defined as the facets are the same since the risks are equal.
	%Since $\risk{\ell}$ is polyhedral, the epigraph of its negation, $E_\ell$, has a finite set of facets, which by definition have well-defined interiors.  For each facet, there must then be some distribution $p_r$ and report $r \in \R$ such that the hyperplane $p_r \mapsto (p_r, \inprod{p_r}{-\ell(r)})$ uniquely supports $E_\ell$.  Form $\Sc$ from the set of such reports $r$, iterating over each facet.  We have $\Sc$ representative for $\ell$ since the union of projected epigraph facets equals the simplex, and these facets and their projections are closed. Therefore, every $p \in \simplex$ is contained in some facet of the epigraph, and thus there is some $r \in \Sc$ so that $r \in \gamma(p)$.
%As the risks are equal, the same is true for $E_L$, e.g., for each facet, there is some $u_r$ so that $p_r \mapsto (p_r, \inprod{p_r}{L(u_r)})$, and one can construct the embedding $\varphi: r \mapsto u_r$ for each $r \in \Sc$.
}

\proposedadd{To verify matching losses, observe $\risk \ell (\delta_y) = \risk L (\delta_y)$ for each $y \in \Y$, and these risks are attained by some report $r$ and its embedding $u_r$, respectively.
Matching optimality is true by construction, since the optimal reports support the epigraph of negative Bayes risk on exactly the same distributions, meaning a report and its embedding are optimal at exactly the same distributions.}\jessie{This feels like it's missing a detail about how $\Sc$ is minimal.}
\end{proof}

@@

\raft{I wonder if we should demote this to a corollary.  We can write the proof of the reverse implication in Proposition~\ref{prop:embed-bayes-risks} like this: first show that if $\risk{L}$ is polyhedral, there is a finite $\U$ which is representative for $L$.  Then show that if $\risk{\ell} = \risk{L}$ then there is some $\Sc$ that is bijective to the particular $\U$ we constructed.  I'm not sure how this will go, but perhaps worth a try, since it would avoid the proof duplication too!}
\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss $\ell : \R \to \reals^\Y_+$ if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and polyhedral.
  For the converse, let $\risk{L}$ be polyhedral.%; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  \proposedadd{Form the set $\Sc := \Sc(L)$ as in Definition~\ref{cons:rep-set}.
  %For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.  Take $\Sc$ to be the collection of such reports $u$, and observe $\Sc$ is representative for $L$.  
  By Corollary~\ref{cor:representative-embeds-restriction}, $L$ embeds $L|_\Sc$, which is finite by construction.}
%  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
%  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
%  Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
\end{proof}

@@

\proposedadd{Moreover, to construct an embedding of dimension $n-1$ instead of $n$ (see~\citet{finocchiaro2020embedding} for significance of dimension),  we use the same technique as in the proof of Proposition~\ref{prop:embed-bayes-risks}.
Consider some invertible linear transformation $A : \reals^n \to \reals^{n-1}$ that reduces to an affine subspace.
Take $L' : \reals^{n-1} \to \reals^\Y$ as $x \mapsto L(A^{-1}(x))$ and $L$ defined as above, so that $\inprod{\ell(r)}{p} = \inprod{L(\varphi(r))}{p} = \inprod{L'(A^{-1}(\varphi(r)))}{p} $ for all $p \in \simplex$.
The Bayes risks $\risk{L}(p)$ and $\risk{L'}(p)$ are equal for all $p \in \simplex$; thus, the result holds in $n-1$ dimensions as well.}\jessiet{Leaving this change in the macro for proofreading.}

@@

\begin{lemma}\label{lem:embed-defs-equiv}
	%  \raft{Introduce $L$}
	Let $L : \reals^d \to \reals^\Y_+$ be a loss function whose infimum is attained in expectation for all $p \in \simplex$.
	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell:\R \to \reals^\Y_+$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
\end{lemma}
\begin{proof}
	\raft{All the important pieces are here, but take it slower.  State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.  Now very similar to the proof of Prop 1 forward direction.}}
	Consider the embedding $\varphi$ given by the property embedding and take the discrete loss $\ell:r \mapsto L(\varphi(r))$.
	Now, we claim that $L$ embeds $\ell$, and by Proposition~\ref{prop:embed-bayes-risks}, we can simply show $\risk{L} = \risk{\ell}$, and the risks being polyhedral follows from $\ell$ being discrete.

	First, we show that for all $p \in \simplex$, we have $(1) \inf_{u \in \reals^d}\inprod{p}{L(u)} = (2) \inf_{r \in \R}\inprod{p}{L(\varphi(r))}$, and the equality of risks follows.
	$(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$ and definition of infimum. 
	Consider that if we had $(1) < (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$, and therefore, we would have $\gamma(p) = \emptyset$, yielding a contradiction. 
	This gives us $(1) = (2)$, so we have $\risk{L} = \risk{L|_{\varphi(\R)}} = \risk{\ell}$.
	%
	%Now consider the property $\Gamma' := p \mapsto \Gamma(p) \cap \varphi(\R)$.
	%We have $\Gamma'$ nondegenerate since $\Gamma$ embedding $\gamma$ implies that, for all $p \in \simplex$, there is some $r \in \R$ such that $\varphi(r) \in \Gamma(p)$.
	%Therefore, for all $p \in \simplex$, we have $\inf_{r \in \R}\inprod{p}{L(\varphi(r))} = \inf_{r \in \R} \inprod{p}{\ell(r)}$, which yields $\risk{L|_{\varphi(\R)}} = \risk{\ell}$.
	%Chaining the two equalities, we now have $\risk{L} = \risk{\ell}$.

@@

@@

\btw{JESSIE: Figures/an example might help clarify this}
When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
\jessiet{This lemma new to journal version}
\begin{lemma}\label{lem:embedded-level-sets-trim}
	Let $\Gamma$ be an elicitable property.
	If $\Gamma$ embeds a (non-redundant) finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)\proposedadd{=\trim(\gamma)}$.
	\proposedadd{RETRY: Let $\Gamma$ be an elicitable property.
		If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then there is a set $\Sc$ such that $\Sc$ is representative for $\gamma$ and $\{\gamma_r : r \in \Sc\} = \{\Gamma_u : u \in \varphi(\Sc)\} = \trim(\Gamma)=\trim(\gamma)$.}
\end{lemma}
\begin{proof}
	Let $L$ elicit $\Gamma$.
	Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
	Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
	%\raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
	As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional in $\affhull(\simplex)$. 
	For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
	Moreover, we have $\{\gamma_r : r \in \R\} = \{\Gamma_{\varphi(r)} : r \in \R\}$ as a corollary since this is true for each $r \in \R$.
	\raft{The main action is here.  (1) Epigraph of $-\risk{L}$. (2) There is really only one case: every level set is a face of the power diagram, which must be contained (weakly, so $\subseteq$) in a facet. (3) To show that level sets are faces, you'll want to appeal to some piece of a proof in the prev section.}
	Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $-\risk{L}$, which is convex, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered as faces of the epigraph of $-\risk{L}$, and therefore a face of the induced power diagram.
	Therefore, we remove lower-dimensional faces, as they are proper subsets of the level sets of embedded reports, and conclude such $\Gamma_u \not \in \trim(\Gamma)$.
	% in one of two cases:
	%First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
	%Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.

@@

\proposedadd{First, construct $\Sc := \Sc(L)$ as Definition~\ref{cons:rep-set}; this is a minimal representative set in the sense that removing any element $r$ corresponding to the facet $F_r$ from $\Sc$ leads to $\gamma(p) \cap \Sc = \emptyset$ for all $p \in \inter{F_r}$. Moreover, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, and therefore $\gamma_r = \Gamma_{\varphi(r)}$, yielding $\{\gamma_r \mid r \in \Sc\} = \{\Gamma_{\varphi(r)} \mid r \in \Sc\}$ as this is true for all $r \in \Sc$.}

\proposedadd{Now let $T := \{\gamma_r \mid r \in \Sc\} = \trim(\gamma)$. 
	First, if $\gamma_r \in T$, then it is not a subset of any level set as $\gamma_r$ is full-dimensional in the simplex as it corresponds to a facet of the epigraph of the negative risk $E_\ell$, and the supporting hyperplane is therefore unique.
	Now, if $\theta \in \trim(\gamma)$, then there is some report $r'$ such that $\theta = \gamma_{r'}$.
	If $r' \not \in \Sc$, we want to claim there is some $r$ such that $\gamma_{r'} = \gamma_r$.
	As $\theta$ is a maximal level set, it has a nonempty interior.
	Therefore, for any $p \in \inter{\theta}$ (and one such $p$ must exist), the hyperplane $p \mapsto (p, \ell(r'))$ uniquely supports the epigraph of negative risk.
	If $r' \not \in \Sc$, then there must be some $r \in \Sc$ such that $p \mapsto (p, \ell(r))$ also supports the same facet of $E_\ell$; if no such $r \in \Sc$ existed, we would contradict our claim that $\Sc$ is representative for $\ell$.
Similarly, we have $\{\Gamma_u \mid u \in \varphi(\Sc)\} = \trim(\Gamma)$ by the same logic.}
\end{proof}
